formula1

### 2019-12-16 inst/formula1.Rmd
use inc and dec

      ## The first choice among eligible players has +1 power on the
      ## numerator:
      F1[which(d==1)] %<>% "+"(1)

      ## denominator of all eligible players; power -1
      F1[eligible] %<>% "-"(1)

@@

      ## everyone moves down the list, so who *was* in second place
      ## becomes first place, who *was* third place becomes second,
      ## and so on:
      d[d>0] %<>% "-"(1)

>>>>

      ## The first choice among eligible players has +1 power on the
      ## numerator:
      F1[which(d==1)] %<>% inc

      ## denominator of all eligible players; power -1
      F1[eligible] %<>% dec

@@

      ## everyone moves down the list, so who *was* in second place
      ## becomes first place, who *was* third place becomes second,
      ## and so on:
      d[d>0] %<>% dec
